---
title: "Session7 In-Session Coding Exercise"
author: "Sunny"
date: "10/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=T, include=FALSE}
## 0. General setups as usual
## References: https://www.princeton.edu/~otorres/DID101R.pdf; https://dhicks.github.io/2018-10-10-did/
##Set your own directory
# setwd("~/AAE636/Session7")
rm(list=ls())

##Install Wooldridge data
library(dplyr)# this is for mutate function
library(magrittr) # this is for the Pipe function %>%
library(psych)
library(foreign)# this package contains read.dta command
library(car)
library(data.table)
library(ggplot2)
library(RCurl)# For the robust SE method 1
library(lmtest) #For the robust SE method 2
library(sandwich) #For the robust SE method 2
```

### 1. Diff-in-Diff

Example Code:
```{r}

# Getting sample data.
mydata = read.dta("http://dss.princeton.edu/training/Panel101.dta")

# Create a dummy variable to indicate the time when the treatment started. Lets assume that treatment started in 1994. In this case, years before 1994 will have a value of 0 and the year of 1994 and years after 1994 will have a value of 1. 
mydata$time = ifelse(mydata$year >= 1994, 1, 0)

# Create a dummy variable to identify the group exposed to the treatment. In this example lets assumed that countries with code country code "E", "F" and "G" were treated (=1).
mydata$treated = ifelse(mydata$country == "E" |
                        mydata$country == "F" |
                        mydata$country == "G", 1, 0)

# Create an interaction between time and treated. We will call this interaction "did".
mydata$did = mydata$time * mydata$treated

mydata = mydata %>%
    mutate(treated.log = (country ==  "E" |
                          country == "F" |
                          country == "G"))

#Not a great example for the DID model, you should justify the control group by proving the parrallel trend before applying DID model.

ggplot(mydata, aes(year, y, color = treated.log)) +
    geom_point(aes(col=treated.log)) +
    stat_summary(geom = 'line') +
    geom_vline(xintercept = 1994) +
    theme_minimal()

```

```{r }
# Estimating the DID model
# Method 1.
didreg <- lm(y ~ treated + time + did, data = mydata)
summary(didreg)

# Method 2.
didreg1 <- lm(y ~ treated*time, data = mydata)
summary(didreg1)

```
#### 2. Heteroskedesticity and Robust Standard Errors

Example code:
```{r}

#Method 1: this will generate the same result as stata
# import the function from repository
url_robust <- "https://raw.githubusercontent.com/IsidoreBeautrelet/economictheoryblog/master/robust_summary.R"
eval(parse(text = getURL(url_robust, ssl.verifypeer = FALSE)),envir=.GlobalEnv)

summary(didreg1, robust = T)$coefficient

#Method 2:We will see this function again when we talk about the clustered standard errors.
coeftest(didreg1, vcov = vcovHC(didreg1, cluster = "HC0"))

```

#### In-Session Coding:
We are interested in examing the policy effect on whether one family works or not: 
The earned income tax credit (EITC) policy took effect in the year of 1994; and the group that benefited from the policy was the families with dependent children.

##### 1. write down your estimation equation.
$\beta_1year + \beta_2$
##### 2. write the code for your estimation:
```{r}
eitc <- read.dta("./eitc.dta")

## Create the dummies for the time of the treatment and the treatment group.

##variable name: children
eitc <- mutate(eitc, ifelse(children == 0 , 0 ,1))
names(eitc)[12]=  "treated"
##variable name: year
eitc <-  mutate(eitc, ifelse(year < 1994, 0, 1))
names(eitc)[13] = "time"

eitc <- eitc %>%  
    mutate(post93= year >= 1994,
           anykids = children >=1)
## Plot the data to show the change
p <- ggplot(eitc) + aes(year, work, color  = anykids) + #geom_point()+
    stat_summary(geom = 'line') #+
    # geom_vline(xintercept = 1994) +
     theme_minimal()
p
## Run the DID regression
fit1 <- lm(work~treated* time, eitc)
summary(fit1)

```

##### 3. By using your regression equation and estimation results, answer the following questions:

##### a. what is the expected probability of working for one family without children before 1994? what is your estimate?

$$
\begin{eqnarray*}
work  = \beta_1 treated \cdot time + \beta_0
\tag{1-a.}
\end{eqnarray*}
$$

##### b. what is the expected probability of working for one family without children in and after 1994? what is your estimate?

##### c. what is the expected effect of the policy to the group without children?

##### d. what is the expected probability of working for one family with children before 1994? what is your estimate?

##### e. what is the expected probability of working for one family with children in and after 1994? what is your estimate?

##### f.what is the expected effect of the policy to the group with children? what is your estimate?

##### 4. Adding controls for your regression
##### Do you think not adding the controls could bias your estimation results? Explain.
```{r}
## Add education and age: variable name "ed" and "age", in your regression

## Run the DID regression with controls
fit2 <- lm(work~treated*time +ed+age, eitc)
summary(fit2)

```


##### 5. Hypothesis Testing
```{r}
## t-test of the expected effect of age and education on y (the probability of working) are the same.
linearHypothesis(fit2, c("age = ed"))
k <- 3 
n <- dim(eitc)[1]
qf(.95, k, n-k-1)
isTRUE(110.44>qf(.95, k, n-k-1))
## F-test of the expected effect of age and education on y (the probability of working) both equal to 0.
linearHypothesis(fit2, c("age = 0", "ed = 0"))
r1 <- 2#num of restriction,
r2 <- n-k-1 #
F_fit22 <-  isTRUE(71.625 > qf(.95, k, n-k-1))
F_fit22
```

