---
title: "Session9 In-Session Exercise"
author: "Sunny"
date: "11/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=T, include=FALSE}
## 0. General setups as usual
## References: https://sites.google.com/site/econometricsacademy/econometrics-models/panel-data-models;
###############https://bookdown.org/ccolonescu/RPoE4/heteroskedasticity.html.

##Set your own directory
# setwd("~/AAE636/Session8")
# rm(list=ls())

##Install Wooldridge data
library(dplyr)# this is for mutate function
library(magrittr) # this is for the Pipe function %>%
library(psych)
library(foreign)# this package contains read.dta command
library(car)
library(data.table)
library(knitr)
library(ggplot2)

library(lmtest) #for coeftest() and bptest().
library(broom) #for glance() and tidy()
library(car) #for hccm() robust standard errors
library(RCurl)# For the robust SE method 1
library(sandwich)

library(plm)# this package is for panel regression
```

### 1. Heteroskedasticity and Clustered Standard Errors

Example Code:
We are using panel_wage.dta data, and we would like to use the following variables for our regression:

dependent: log(wage): lwage
independent: education: ed; exprience: exp; weeks worked: wks
```{r}
# Getting sample data.
wagedata <- read.dta('panel_wage.dta')
names(wagedata)
head(wagedata)
```

#### 1.1. Test for Heteroskedasticity
```{r }
#Method 1. Graph the residuals
olsfit <- lm(lwage ~ exp, data=wagedata)
summary(olsfit)
residual <- residuals(olsfit)

plot(wagedata$lwage~wagedata$exp, type="p",
     xlab="Experience", ylab="Log(wage)")
abline(olsfit)

plot(residual~wagedata$exp, 
     xlab="Experience", ylab="Residuals")

#Method 2. Breusch-Pagan Test using package
#install.packages("lmtest") #Install this first if you don't have the package
library(lmtest)
bptest(olsfit)

#Method 3. Breusch-Pagan Test using F-test
a <- 0.05
residual.sq <- resid(olsfit)^2
#The test equation:
residual.regression <- lm(residual.sq~exp, data=wagedata)
summary(residual.regression)
n <- dim(wagedata)[1]
F.critical <- qf(1-a, 1, n-1-1)
F.critical

#Method 4. Breusch-Pagan Test using Lagrange Multiplier
Lagrange.stat <- n*summary(residual.regression)$r.squared
Lagrange.stat
chi.critical <-qchisq(1-a, 1)
chi.critical 
pval.chi <- 1-pchisq(Lagrange.stat,1)
pval.chi
```

#### 1.2. Clustered SE
```{r}
#Robust: this will generate the same result as stata
# import the function from repository
url_robust <- "https://raw.githubusercontent.com/IsidoreBeautrelet/economictheoryblog/master/robust_summary.R"
eval(parse(text = getURL(url_robust, ssl.verifypeer = FALSE)),envir=.GlobalEnv)

summary(olsfit)$coefficient

summary(olsfit, robust = T)$coefficient

#Robust = c("HC3", "HC", "HC0", "HC1", "HC2", "HC4", "HC4m", "HC5"),
#clustered SE: just plug in the varible name into the cluster
coeftest(olsfit, vcov = vcovHC(olsfit, cluster = "education"))

```

#### 1.3 Weighted Least Square
When $\sigma_i^2=\sigma^2\cdot exp_i$, correct your estimation using WLS method.

```{r}
#direct usage of weight
wls.fit1 <- lm(lwage ~ exp, data=wagedata, weights = 1/exp)
summary(wls.fit1)

#Mannually transform
wagedata$lwage.star <- wagedata$lwage/sqrt(wagedata$exp)
wagedata$exp.star <- wagedata$exp/sqrt(wagedata$exp)
wagedata$intercept.star <- 1/sqrt(wagedata$exp)
wls.fit2 <- lm(lwage.star~ intercept.star+exp.star-1, data=wagedata)
summary(wls.fit2)
```
#### 1.4 Feasible Generalized Least Square
When $\sigma_i^2=\sigma^2\cdot exp(\delta_1 exp_i+\delta_0)$,correct your estimation using FGLS method.

**Step 1.OLS estimate**
```{r}
summary(olsfit)
residual.sq <- resid(olsfit)^2
```

**Step 2.generate $g_i=log(\hat{\mu^2_i})$**
```{r}
g <- log(residual.sq)
```

**Step 3.predict $\hat{g_i}$**
```{r}
gfit <- lm(g~exp,data = wagedata)
```

**Step 4.change back to exponential**
```{r}
h.hat <- exp(fitted(gfit))
```

**Step 5.weighted least square**
```{r}
fgls.fit <- lm(lwage ~ exp, data=wagedata, weights = 1/h.hat)
fgls.fit
```

### 2. Panel Estimation

```{r}
#install.packages("plm")
#library(plm)
```

#### Set the "group" and "time" variables

same as xtset in Stata, the same id and the t should have no more than one observations.

Group: individual : id

Time: year: t

```{r}
pdata <- plm.data(wagedata, index=c("id","t"))
pdata <- pdata.frame(wagedata,index = c("id","t"),drop.index = TRUE)
```

#### Pooled OLS estimator
```{r}
pooling <- plm(lwage ~ exp+wks+ed, data=pdata, model= "pooling")
summary(pooling, robust = T)$coefficient
coeftest(pooling, vcov = vcovHC(pooling, cluster = "group"))
coeftest(pooling, vcov = vcovHC(pooling, cluster = "time"))
```

#### Between estimator
```{r}
between <- plm(lwage ~ exp+wks+ed, data=pdata, model= "between")
summary(between, robust = T)$coefficient
coeftest(pooling, vcov = vcovHC(pooling, cluster = "group"))
```

#### First differences estimator
```{r}
firstdiff <- plm(lwage ~ exp+wks+ed, data=pdata, model= "fd")
summary(firstdiff, robust = T)$coefficient
coeftest(firstdiff, vcov = vcovHC(firstdiff, cluster = "group"))

#we don't need to include the exp and ed in the regression
firstdiff <- plm(lwage ~ wks, data=pdata, model= "fd")
summary(firstdiff, robust = T)$coefficient
coeftest(firstdiff, vcov = vcovHC(firstdiff, cluster = "group"))
```

#### Fixed effects or within estimator
```{r}
fixed <- plm(lwage ~ wks+ed, data=pdata, model= "within")
summary(fixed, robust = T)$coefficient
coeftest(fixed, vcov = vcovHC(fixed, cluster = "group"))
```

#### Random effects estimator
```{r}
random <- plm(lwage ~ wks+ed, data=pdata, model= "random")
summary(random, robust = T)$coefficient
coeftest(random, vcov = vcovHC(random, cluster = "group"))
```

#### Fixed effects for time and individual
```{r}
twoway.fixed <- plm(lwage ~ wks+ed, data=pdata, model= "within",method="twoways")
summary(twoway.fixed, robust = T)$coefficient
coeftest(twoway.fixed, vcov = vcovHC(twoway.fixed, cluster = "group"))
```

#### Random effects for time and individual
```{r}
twoway.random <- plm(lwage ~ wks+ed, data=pdata, model= "random",method="twoways")
summary(twoway.random, robust = T)$coefficient
coeftest(twoway.random, vcov = vcovHC(twoway.random, cluster = "group"))
```
