---
title: "Session9 In-Session Exercise"
author: "Sunny"
date: "11/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=T, include=FALSE}
## 0. General setups as usual
## References: https://sites.google.com/site/econometricsacademy/econometrics-models/panel-data-models;
###############https://bookdown.org/ccolonescu/RPoE4/heteroskedasticity.html.

##Set your own directory
setwd("~/AAE636/Session8")
rm(list=ls())

##Install Wooldridge data
library(dplyr)# this is for mutate function
library(magrittr) # this is for the Pipe function %>%
library(psych)
library(foreign)# this package contains read.dta command
library(car)
library(data.table)
library(knitr)
library(ggplot2)

library(lmtest) #for coeftest() and bptest().
library(broom) #for glance() and tidy()
library(car) #for hccm() robust standard errors
library(RCurl)# For the robust SE method 1
library(sandwich)

library(plm)# this package is for panel regression
```

### 1. Heteroskedasticity and Clustered Standard Errors

Example Code:
We are using panel_wage.dta data, and we would like to use the following variables for our regression:

dependent: log(wage): lwage
independent: education: ed; exprience: exp; weeks worked: wks
```{r}
# Getting sample data.
wagedata <- read.dta('panel_wage.dta')
names(wagedata)
head(wagedata)
```

#### 1.1. Test for Heteroskedasticity
```{r }
#Method 1. Graph the residuals
olsfit <- lm(lwage ~ exp, data=wagedata)
summary(olsfit)
residual <- residuals(olsfit)

plot(wagedata$lwage~wagedata$exp, type="p",
     xlab="Experience", ylab="Log(wage)")
abline(olsfit)

plot(residual~wagedata$exp, 
     xlab="Experience", ylab="Residuals")

#Method 2. Breusch-Pagan Test using package
#install.packages("lmtest") #Install this first if you don't have the package
library(lmtest)
bptest(olsfit)

#Method 3. Breusch-Pagan Test using F-test
a <- 0.05
############################################
############Your Code Here##################
############################################

#Method 4. Breusch-Pagan Test using Lagrange Multiplier
############################################
############Your Code Here##################
############################################
```

#### 1.2. Clustered SE
```{r}
#Robust: this will generate the same result as stata
# import the function from repository
url_robust <- "https://raw.githubusercontent.com/IsidoreBeautrelet/economictheoryblog/master/robust_summary.R"
eval(parse(text = getURL(url_robust, ssl.verifypeer = FALSE)),envir=.GlobalEnv)

summary(olsfit)$coefficient

summary(olsfit, robust = T)$coefficient

#Robust = c("HC3", "HC", "HC0", "HC1", "HC2", "HC4", "HC4m", "HC5"),
#clustered SE: just plug in the varible name into the cluster
coeftest(olsfit, vcov = vcovHC(olsfit, cluster = "education"))

```

#### 1.3 Weighted Least Square
When $\sigma_i^2=\sigma^2\cdot exp_i$, correct your SE with WLS estimator.

```{r}
#direct usage of weight
############################################
############Your Code Here##################
############################################

#Mannually transform
############################################
############Your Code Here##################
############################################
```
#### 1.4 Feasible Generalized Least Square
When $\sigma_i^2=\sigma^2\cdot exp(\delta_1 exp_i+\delta_0)$,correct the SE of $\beta_1$ using FGLS method.

**Step 1.OLS estimate**
```{r}
############################################
############Your Code Here##################
############################################
```

**Step 2.generate $g_i=log(\hat{\mu^2_i})$**
```{r}
############################################
############Your Code Here##################
############################################
```

**Step 3.predict $\hat{g_i}$**
```{r}
############################################
############Your Code Here##################
############################################
```

**Step 4.change back to exponential**
```{r}
############################################
############Your Code Here##################
############################################
```

**Step 5.weighted least square**
```{r}
############################################
############Your Code Here##################
############################################
```

### 2. Panel Estimation

```{r}
#install.packages("plm")
#library(plm)
```

#### Set the "group" and "time" variables

same as xtset in Stata, the same id and the t should have no more than one observations.

Group: individual : id

Time: year: t

```{r}
pdata <- plm.data(wagedata, index=c("id","t"))
pdata <- pdata.frame(wagedata,index = c("id","t"), drop.index = TRUE)
```

#### Pooled OLS estimator
```{r}
pooling <- plm(lwage ~ wks+ed, data=pdata, model= "pooling")
summary(pooling, robust = T)$coefficient
coeftest(pooling, vcov = vcovHC(pooling, cluster = "group"))
coeftest(pooling, vcov = vcovHC(pooling, cluster = "time"))
```

#### Between estimator
```{r}
between <- plm(lwage ~ wks+ed, data=pdata, model= "between")
summary(between, robust = T)$coefficient
coeftest(pooling, vcov = vcovHC(pooling, cluster = "group"))
```

#### First differences estimator
```{r}
firstdiff <- plm(lwage ~ wks+ed, data=pdata, model= "fd")
summary(firstdiff, robust = T)$coefficient
coeftest(firstdiff, vcov = vcovHC(firstdiff, cluster = "group"))
```

#### Fixed effects or within estimator
```{r}
fixed <- plm(lwage ~ wks+ed, data=pdata, model= "within")
summary(fixed, robust = T)$coefficient
coeftest(fixed, vcov = vcovHC(fixed, cluster = "group"))
```

#### Random effects estimator
```{r}
random <- plm(lwage ~ wks+ed, data=pdata, model= "random")
summary(random, robust = T)$coefficient
coeftest(random, vcov = vcovHC(random, cluster = "group"))
```

#### Fixed effects for time and individual
```{r}
twoway.fixed <- plm(lwage ~ wks+ed, data=pdata, model= "within",method="twoways")
summary(twoway.fixed, robust = T)$coefficient
coeftest(twoway.fixed, vcov = vcovHC(twoway.fixed, cluster = "group"))
```

#### Random effects for time and individual
```{r}
twoway.random <- plm(lwage ~ wks+ed, data=pdata, model= "random",method="twoways")
summary(twoway.random, robust = T)$coefficient
coeftest(twoway.random, vcov = vcovHC(twoway.random, cluster = "group"))
```

#### First differences estimator and more

Suppose the sample contains only working people and the experience increase one as one year goes by, adding the experience variable into the Panel regression using first difference method, interpret each of the coefficients.

```{r}
firstdiff <- plm(lwage ~ exp+wks+ed, data=pdata, model= "fd")
summary(firstdiff, robust = T)$coefficient
coeftest(firstdiff, vcov = vcovHC(firstdiff, cluster = "group"))
```