---
title: "Session2"
author: "Sunny"
date: "9/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 0. Set your own directory and load the data

```{r}
getwd()
library(wooldridge)
setwd("/Users/fyenne/R_hahaha/R_lab/Lab 2")
data <- wage2
names(data)
dim(data)[1]
mean(age)
sd(wage)
mean(wage[tenure<5])
B <-  mean(exper[married==1])
B
lm.fit <- lm(formula = wage ~ educ, data = data)
summary(lm.fit)  # 斜率

```

## 1. Take a look at your data

a. How many observations are in the dataset?
b. What is the sample mean of age?
c. What is the standard deviation of monthly wages?
d. What is the average monthly wages of individuals with LESS THAN FIVE years of job tenure?
e. What is the sample mean of experience for workers who are married?

```{r data}
attach(data)
names(data)
dim(data)[1]
mean(age)
sd(wage)
mean(wage[tenure<5])
B <-  mean(exper[married==1])
B
```

## 2. OLS: The Best Linear Unbiased Estimator
Why do we care about the unbiasness, consistency, and #efficiency?

### one parameter example
```{r}
lm.fit <- lm(formula = wage ~ educ, data = data)
lm.fit2 <- lm(formula = wage ~ ., data = data)
summary(lm.fit)
p1 <-ggplot(wage2 ,aes(wage, educ)) + geom_point() + geom_smooth(method = "lm", 
                                                              )
```


```{r}
estimate <- predict(lm.fit)
estimate2 <- lm.fit$fitted.values
identical(estimate,estimate2)

#residuals  # lm.fit <- lm(formula = wage ~ educ, data = data)
mu <- residuals(lm.fit)
mu2 <- lm.fit$residuals
identical(mu,mu2)

#estimated coefficients
beta <- lm.fit$coefficients

#numeric properties
xmu<-educ*mu
yhatmu<-estimate*mu
ymu<-wage*mu
mumu<-mu*mu
sum(mu)# almost 0
sum(xmu)# almost 0
sum(yhatmu)# almost 0
sum(ymu)# what is this?
sum(mumu)
```
### Hypothesis Testing and Confidence Intervals

```{r}
#z-statistics and t-statistics：
qnorm(1-.05/2)#z-statistics
qt(1-.05/2,30)#t-statistics , significants level
qt(1-.05/2,200)
qt(1-.05/2,2000)
```

### Example: Genarate the two-tailed 95% CI for married people's wage

```{r}
x<-wage[married==1]

mwage<-mean(x)
sdmwage<-sd(x)
lenm<-length(x)

z<-qnorm(1-.05/2)

dof<-lenm-1
t<-qt(1-.05/2,dof)

CI <- c(mwage-z*sdmwage/sqrt(lenm),mwage+z*sdmwage/sqrt(lenm))
CI
CI <- c(mwage-t*sdmwage/sqrt(lenm),mwage+t*sdmwage/sqrt(lenm))
CI

```

### Example: Hypothesis test
Test if the wage mean of the married people is equal to 900:
NULL Hypothesis $H_0$: $mwage=900$

Alternative Hypothesis $H_1$: $mwage\neq 900$

```{r}
#One step method
t.test(x,mu = 900)

#Step by Step method
t.estimate<-(mwage-900)/(sdmwage/sqrt(lenm))
t.estimate

isTRUE(t.estimate>z)

isTRUE(t.estimate>t)

#--------------------------------------------
#--------------------------------------------

# t.test(x, …)
# # S3 method for default
# t.test(x, y = NULL,
#        alternative = c("two.sided", "less", "greater"),
#        mu = 0, paired = FALSE, var.equal = FALSE,
#        conf.level = 0.95, …)
# 
# # S3 method for formula
# t.test(formula, data, subset, na.action, …)
#--------------------------------------------

# ols(formula, data, weights, subset, na.action=na.delete, 
#     method="qr", model=FALSE,
#     x=FALSE, y=FALSE, se.fit=FALSE, linear.predictors=TRUE,
#     penalty=0, penalty.matrix, tol=1e-7, sigma,
#     var.penalty=c('simple','sandwich'), …)
#--------------------------------------------

# predict 
# Make a Raster object with predictions from a fitted model object
# predict(object, model, filename="", fun=predict, ext=NULL, 
#    const=NULL, index=1, na.rm=TRUE, inf.rm=FALSE, factors=NULL, 
#    format, datatype, overwrite=FALSE, progress='', ...)
#--------------------------------------------
# identical
#  The safe and reliable way to test two objects for being exactly equal.
# identical(x, y, num.eq = TRUE, single.NA = TRUE, attrib.as.set = TRUE,
           # ignore.bytecode = TRUE, ignore.environment = FALSE,
          # ignore.srcref = TRUE)
#--------------------------------------------
#--------------------------------------------
```
```

