---
title: "Session8 In-Session Exercise"
author: "Sunny"
date: "11/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=T, include=FALSE}
## 0. General setups as usual
## References: https://sites.google.com/site/econometricsacademy/econometrics-models/panel-data-models;
###############https://bookdown.org/ccolonescu/RPoE4/heteroskedasticity.html.

##Set your own directory
# setwd("~/AAE636/Session8")
# rm(list=ls())

##Install Wooldridge data
library(dplyr)# this is for mutate function
library(magrittr) # this is for the Pipe function %>%
library(psych)
library(foreign)# this package contains read.dta command
library(car)
library(data.table)
library(knitr)
library(ggplot2)

library(lmtest) #for coeftest() and bptest().
library(broom) #for glance() and tidy()
library(car) #for hccm() robust standard errors
library(RCurl)# For the robust SE method 1
library(sandwich)

library(plm)# this package is for panel regression
```

### 1. Heteroskedasticity and Clustered Standard Errors

Example Code:
We are using panel_wage.dta data, and we would like to use the following variables for our regression:

dependent: log(wage): lwage
independent: education: ed; exprience: exp; weeks worked: wks
```{r}
# Getting sample data.
wagedata <- read.dta('panel_wage.dta')
names(wagedata)
head(wagedata)
```

#### 1.1. Test for Heteroskedasticity
```{r }
#Method 1. Graph the residuals
olsfit <- lm(lwage ~ exp+wks+ed, data=wagedata)
summary(olsfit)
residual <- residuals(olsfit)

plot(residual~wagedata$ed, xlab="Education", ylab="Residuals")
plot(residual~wagedata$exp, xlab="Experience", ylab="Residuals")

#Method 2. Breusch-Pagan Test
#install.packages("lmtest") #Install this first if you don't have the package
library(lmtest)
bptest(olsfit)
# A p-Value > 0.05 indicates that the null hypothesis(the variance is unchanging in the residual) can be rejected and therefore heterscedasticity exists. This can be confirmed by running a global validation of linear model assumptions (gvlma) on the lm objec
```

#### 1.2. Clustered SE
```{r}
#Robust: this will generate the same result as stata
# import the function from repository
url_robust <- "https://raw.githubusercontent.com/IsidoreBeautrelet/economictheoryblog/master/robust_summary.R"
eval(parse(text = getURL(url_robust, ssl.verifypeer = FALSE)),envir=.GlobalEnv)

summary(olsfit)$coefficient

summary(olsfit, robust = T)$coefficient

Robust = c("HC3", "HC", "HC0", "HC1", "HC2", "HC4", "HC4m", "HC5")
#clustered SE: just plug in the varible name into the cluster
coeftest(olsfit, vcov = vcovHC(olsfit, cluster = "education"))

```

### 2. Panel Estimation

```{r}
#install.packages("plm")
#library(plm)
```

#### Set the "group" and "time" variables

same as xtset in Stata, the same id and the t should have no more than one observations.

Group: individual : id

Time: year: t
```{r}
pdata <- plm.data(wagedata, index=c("id","t"))
pdata <- pdata.frame(wagedata,index = c("id","t"), drop.index = TRUE)
```

#### Pooled OLS estimator
```{r}
pooling <- plm(lwage ~ exp+wks+ed, data=pdata, model= "pooling")
summary(pooling, robust = T)$coefficient
coeftest(pooling, vcov = vcovHC(pooling, cluster = "group"))
coeftest(pooling, vcov = vcovHC(pooling, cluster = "time"))
```

#### Between estimator
```{r}
between <- plm(lwage ~ exp+wks+ed, data=pdata, model= "between")
summary(between, robust = T)$coefficient
coeftest(pooling, vcov = vcovHC(pooling, cluster = "group"))
```

#### First differences estimator
```{r}
firstdiff <- plm(lwage ~ exp+wks+ed, data=pdata, model= "fd")
summary(firstdiff, robust = T)$coefficient
coeftest(firstdiff, vcov = vcovHC(firstdiff, cluster = "group"))

#we don't need to include the exp and ed in the regression
firstdiff <- plm(lwage ~ wks, data=pdata, model= "fd")
summary(firstdiff, robust = T)$coefficient
coeftest(firstdiff, vcov = vcovHC(firstdiff, cluster = "group"))
```

#### Fixed effects or within estimator
```{r}
fixed <- plm(lwage ~ exp+wks+ed, data=pdata, model= "within")
summary(fixed, robust = T)$coefficient
coeftest(fixed, vcov = vcovHC(fixed, cluster = "group"))
```

#### Random effects estimator
```{r}
random <- plm(lwage ~ exp+wks+ed, data=pdata, model= "random")
summary(random, robust = T)$coefficient
coeftest(random, vcov = vcovHC(random, cluster = "group"))
```

#### Fixed effects for time and individual
```{r}
twoway.fixed <- plm(lwage ~ exp+wks+ed, data=pdata, model= "within",method="twoways")
summary(twoway.fixed, robust = T)$coefficient
coeftest(twoway.fixed, vcov = vcovHC(twoway.fixed, cluster = "group"))
```

#### Random effects for time and individual
```{r}
twoway.random <- plm(lwage ~ exp+wks+ed, data=pdata, model= "random",method="twoways")
summary(twoway.random, robust = T)$coefficient
coeftest(twoway.random, vcov = vcovHC(twoway.random, cluster = "group"))
```

### 3. In-Session Exercise
#### First differences estimator
1. Write down the regression equations for this model, the regressors we are using is ***exp, exp2(experience square), wks, and ed***, make proper assumptions to identify the coefficient for experience. Hints: experience increases one together with the year.

2. Interpret each of the coefficients of the regression.

```{r}
firstdiff <- plm(lwage ~ exp+exp2+wks+ed, data=pdata, model= "fd")
summary(firstdiff, robust = T)$coefficient
coeftest(firstdiff, vcov = vcovHC(firstdiff, cluster = "group"))
```