---
title: "Session6 In-Session Coding Exercise"
author: "Sunny"
date: "10/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=T, include=FALSE}
## 0. General setups as usual
##Set your own directory
# setwd("~/AAE636/Session6")
# rm(list=ls())

##Install Wooldridge data
library("wooldridge")
library(psych)
library(foreign)# this package contains read.dta command
library(car)
library(data.table)

data <- sleep75
```


### Tips for reading the csv file or dta file

```{r}
cpsdata <- read.csv('../636_as4/cps_extract_2004.csv',header = T)
names(cpsdata)
# cpsdata <- read.dta('cps_extract_2004.dta')
# names(cpsdata)

```

## 1. Elasticity and Log/Level Regression
level-level model y~x： one unit change in x leads to $\beta_1$ unit change in the conditional expection of y.

```{r}
names(data)
totwrk <- totwrk+1
earns74 <- earns74+1
fit1 <- lm(totwrk~earns74)
fit1$coefficients
```


log-level model ln(y)~x： one unit change in x leads to $(100*\beta_1)\%$ change in the conditional expection of y.
```{r}
logtotwrk <- log(totwrk)
logearns <- log(earns74)
fit2 <- lm(logearns~totwrk)
fit2$coefficients
```

log- log model ln(y)~ln(x)： 1% change in x leads to $\beta_1\%$ change in the conditional expection of y.
```{r}
fit3 <- lm(logearns~logtotwrk)
fit3$coefficients
```


level-log model y~ln(x)： 1% change in x leads to $(\beta_1/100)\%$change in the conditional expection of y.
```{r}
fit4 <- lm(earns74~logtotwrk)
fit4$coefficients
```

#### We have a problem here: there are 0s in our **totwrk**.

One simple way is just to drop it and run seperate regressions for the dropped sample since their elasticity doesn't follow our linear regression (log0 is -Inf).The other way is to transform your data a bit, such as adding 1 to the total work time, but the interpretation is different. Here we just drop it.

### a. Level-Level regression


#### Coding exercise: Calculate elasticity at the mean

```{r}
El.etotwrk <- fit1$coefficients[2]*mean(totwrk)/mean(earns74)
El.etotwrk
```


```{r}
level.level.fit <- lm(slpnaps~totwrk,data = sleep75)
summary(level.level.fit)
#Calculate elasticity at the mean.
El.sltotwrk <- level.level.fit$coefficients[2]*mean(totwrk)/mean(slpnaps)
El.sltotwrk
```

### b. Log-Level regression

#### Coding exercise: Calculate elasticity at the mean

```{r}

sleep75$log.totwrk <- log(sleep75$totwrk)
sleep75$log.slpnaps <- log(sleep75$slpnaps)
log.level.fit <- lm(log.slpnaps~totwrk,data = sleep75)
summary(log.level.fit)
#Calculate elasticity at the mean.
attach(sleep75)
El.logsltot <- log.level.fit$coefficients[2] *mean(log.totwrk)/mean(log.slpnaps)
El.logsltot 
```

### c. Level-Log regression

#### Coding exercise: Calculate elasticity at the mean

```{r}
dim(sleep75)
level.log.fit <- lm(slpnaps~log.totwrk,data = sleep75,subset = totwrk>0)
summary(level.log.fit)
#Calculate elasticity at the mean
sleep75 <- filter(sleep75, totwrk>0)
El.c1 <- level.log.fit$coefficients[2]*mean(log.totwrk)/mean(slpnaps) 

# this x is not equal to the beta1 hat
El.c1
```

### d. Log-Log regression

#### Coding exercise: Calculate elasticity

```{r}
log.log.fit <- lm(log.slpnaps~log.totwrk,data = sleep75,subset = totwrk>0)
summary(log.log.fit)
#Report the elasticity
El.d1 <- log.log.fit$coefficients[2]
El.d1
```

#### Compare the 4 elasticity results

## 2. Higher Orders

#### Coding exercise: Calculate the expected change in sleep time for someone going from 12 year of education to 16 years of education.

```{r}
rm(list = ls())
sleep75$totwrksq <- (sleep75$totwrk)^2
square.fit <- lm(slpnaps~totwrk+totwrksq,data = sleep75)
summary(square.fit)

```


# 3. Dummy Variables

#### Coding Exercise: Calculate the expected difference of sleeping time for women and men conditional on the same total working time.

```{r}
dummy.fit <- lm(slpnaps~totwrk+male,data = sleep75)
summary(dummy.fit)

```

### Generate the categorical dummy variables

#### Coding Exercise: Generate the dummies for education: 

MiddleSchool: education<9;
HighSchool: 9<=education<12;
Undergraduate: 12<=education<16;
Graduate: education>=16;
```{r}
#Generate the dummies
rm(list=ls())
data <- sleep75

MiddleSchool <- filter(sleep75, educ<9)
HighSchool <-filter(sleep75, educ== c(9:11))
Undergraduate <- filter(sleep75, educ==c(12:16))
Graduate <-filter(sleep75, 16<educ)
 
MiddleSchool <- as.numeric(sleep75$educ<9) #dummy variables
summary(MiddleSchool)
mutate()
#Use MiddlesSchool as the reference
#cate.fit <- lm(slpnaps~totwrk+HighSchool+Undergraduate+Graduate,data = sleep75)
#summary(cate.fit)
```


#### Coding Exercise: Test the null hypothesis that: Graduates have the same sleep time as the HighSchool students conditional on that they work the same time at 0.05 significance level.

```{r}
# t.stat <- 

# critical value

# results

```

### 4. Regression without intercepts

#### Compare the results. 

No intercepts are a very strong assumption. 

```{r}
no.fit <- lm(slpnaps~totwrk-1,data = sleep75)  # no interceptiong  -1
summary(no.fit)
summary(level.level.fit)

```